Footpath Planning for Example-driven Procedural Road Networks

### 2020-03-17 paper/paper.tex
Add a section about relative overlap and semantic accuracy

>>>>

The relative overlap may also be used to determine building matching relations even when the semantic accuracy is low. If a large building is represented by a single footprint in one dataset but by several smaller footprints in the other, XXX found that if $S_{RO}(foot_{A}, foot_{B}) < 30\%$ for two buildings $A$ and $B$ from different sets, then $A$ and $B$ are highly likely to be separate, neighbouring buildings and not in fact identical. Therefore we will here assume that two buildings are matching candidates if their relative area overlap is greater than 30\%. If a one-to-many object matching is found, the compound perimeter of the footprints in the many-set will be used when calculating the turning function and finding closest vertices between the polygons.
